\documentclass{resume} 
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in,a4paper]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Andreas Rossi Dewantara} % Your name
\address{Jl. Denpasar Raya No. Kav. 5, Kuningan, Karet Kuningan, Setiabudi, South Jakarta 12950} 
\address{(+62)856 4750 6009 \\ dewantara@kemenkeu.go.id}

\begin{document}

\begin{rSection}{Education}


{\bf STAN State Finance Polytechnic (Politeknik Keuangan Negara-STAN)} \hfill {\em 2015-2017} 
\\ Bachelor of Applied Sciences, Accounting.\hfill { Overall GPA: 3.69/4.00 }

{\bf State College of Accountancy (Sekolah Tinggi Akuntansi Negara)} \hfill {\em 2008-2011} 
\\ Diploma, Taxation Administration.\hfill { Overall GPA: 3.41/4.00 }

\end{rSection}

\begin{rSection}{Work Experience}
\begin{rSubsection}{Directorate of International Taxation}{2017-present}{Senior Analyst for Transfer Pricing and International Tax}{}
 \item Handling Advance Pricing Agreement (APA)/Mutual Agreement Procedure (MAP) cases. Indonesian delegation for Competent Authority meetings with tax authority from European countries.
 \item Person-in-charge for Indonesia at the Organisation for Economic Co-operation and Development (OECD) Working Party No. 6 (Taxation of Multinational Enterprises).
 \item Analyst for Directorate General of Taxes (DGT) Transfer Pricing Task Force which collectively realised tax revenues of 2.99 trillion IDR (approximately 213 million USD) in 2020.
 \item Analyst for Country-by-Country Report (CbCR) Team, developing CbCR Compliance Risk Management system and preparing statistics for OECD Corporate Tax Statistics.
 \item Involved in the drafting of Indonesian regulations concerning transfer pricing, APA/MAP, and CbCR.
\end{rSubsection}
\begin{rSubsection}{Foreign Investment Tax Office 2}{2013-2015}{Operator Console}{}
 \item Assisting foreign investment companies to fulfil their tax obligation as well as handling various requests as part of service to the taxpayers.
 \item Processing internal taxation data and external/other third-party data to support accounts representative and tax auditors in monitoring taxpayer compliance.
\end{rSubsection}
\end{rSection}

\begin{rSection}{Publication}
\begin{rSubsection}{Published/Accepted Journal Article}{}{}{}
 \item Daholi, T. Q. H and \textbf{A. R. Dewantara.} (2020) “New Development and Analyses on Indonesia’s Transfer Pricing Regulation” \textit{Asia-Pacific Tax Bulletin}. Vol. 26, No. 4, International Bureau of Fiscal Documentation.
\end{rSubsection}
\begin{rSubsection}{Conference Paper}{}{}{}
\item Daholi, T. Q. H and \textbf{A. R. Dewantara.} (2020) “’The Road Not Taken’: Unlocking the Conundrums of Transfer Pricing Dispute in Indonesia” \textit{Tax Administration Research Center (TARC) 8\textsuperscript{th} Annual Conference}. University of Exeter, UK.
\item \textbf{Dewantara, A. R.} (2020) “Analysis of Misaligned Profits and Tax Risks from Aggregated and Anonymised Country-by-Country Report” \textit{National Taxation Conference (Konferensi Nasional Perpajakan) 2020}. Directorate General of Taxes, Jakarta, Indonesia.
\item \textbf{Dewantara, A. R.} and Riandoko, R. (2017) “Bad Leader For Bad Game: Empirical Study of Harmful Tax Competition in ASEAN Countries Using Nash-Stackelberg Competition Approach” \textit{Australasian Tax Teachers Association (ATTA) Conference 2018}. Monash University, Australia.
\end{rSubsection}
\end{rSection}
\newpage
\begin{rSection}{Professional Training}
{$\diamond$ Joint DGT - OECD Workshop on Advanced Tax Treaties} \hfill\mbox{\em Indonesia, 2019} 

{$\diamond$ Joint DGT - OECD Workshop on Transfer Pricing} \hfill\mbox{\em Indonesia, 2019} 

{$\diamond$ Joint OECD - Intra-European Organisation of Tax Administrations Training\\ on Handling Mutual Agreement Cases}\hfill\mbox{\em Hungary, 2018}

{$\diamond$ Joint DGT - Netherlands Tax and Customs Administration Workshop on\\ Resolution of Disputes on Taxation Issues} \hfill\mbox{\em Indonesia, 2018}

{$\diamond$ Joint DGT - Japan International Cooperation Agency Workshop on Transfer\\ Pricing: Recent Updates on BEPS} \hfill\mbox{\em Indonesia, 2018}
\end{rSection}

\begin{rSection}{Organisational Experience} 
\item Co-founder of INFINITE/Indonesian Institute for International Taxation Studies, 2019.
\item Organiser of “Tax Café”, a collaboration with Center for Indonesia Taxation Analysis (CITA), 2017.
\item Member of Pusat Studi Perpajakan (Taxation Research Center) PKN-STAN, 2017.
\item Co-founder and editor of Birokreasi, 2013.
\item Vice President of STAN English Club, 2010-2011.
\end{rSection}

\begin{rSection}{Personal Skills}

\begin{tabular}{p{4cm}p{12.6cm}}
\textbf{Languages} & Indonesia (native), English (proficient) \\
\textbf{Job-related} & Transfer pricing, tax treaty, CbCR, APA, MAP\\
\textbf{Statistical software} & Stata (intermediate), R (basic), EViews (basic), gretl (basic), SPSS (basic) \\
\textbf{Office suite} & Excel, Word, PowerPoint (proficient), Access (basic)\\
\textbf{Other} & Python (basic), Tableau (basic), {\LaTeX} (basic)\\

\end{tabular}

\end{rSection}


\end{document}